\Large \bf Dismal Code: Studying the Evolution of Security Bugs

### 2013-09-26 docs/evol.tex
fixed authors, pics

\author{
{\rm Dimitris Mitropoulos}\\
Department of Management Science and Technology,
Athens University of Economics and Business
\and
{\rm Vassilios Karakoidas}\\
Department of Management Science and Technology,
Athens University of Economics and Business
\and
{\rm Panos Louridas}\\
Department of Management Science and Technology,
Athens University of Economics and Business
\and
{\rm Georgios Gousios}\\
Software Engineering Research Group,
Delft University of Technology
\and
{\rm Diomidis Spinellis}\\
Department of Management Science and Technology,
Athens University of Economics and Business
}

@@

\begin{figure}[t]
  \begin{center}
    \includegraphics[scale=0.75]{figures/arch.pdf}
  \end{center}
  \caption{The Data Processing Architecture}
  \label{fig:arch}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[scale=0.42]{version_count.pdf}
	\caption{Distribution of Version Count Among Project Population}
	\label{fig:version-count}
\end{figure}

@@

\begin{table*}[t]
\centering
\caption{Bug Categorisation According to FindBugs}
\label{tbl:bug-cat}
\begin{tabular}{l p{35em}}
\hline
Category & Description\\
\hline
Bad Practice & Violations of recommended and essential
coding practice. \\
Correctness & Involves coding misting a way that is particularly different from the other bug sakes resulting in code
that was probably not what the developer intended. \\
Experimental & Includes unsatisfied obligations. For instance,
forgetting to close a file. \\
Internationalization (i18n) & Indicates the use of non-localized methods. \\
Multi-Threaded ({\sc mt}) Correctness & Thread synchronization issues. \\
Performance & Involves inefficient memory usage allocation, usage 
of non-static classes. \\
Style & Code that is confusing, or
written in a way that leads to errors.\\
Malicious Code & Involves variables or fields exposed to classes that should
not be using them. \\
Security & Involves input validation issues, unauthorized database connections
and others. \\
\hline
\end{tabular}
\end{table*}

@@

\begin{figure}[t]
	\centering
	\includegraphics[scale=0.39]{bug_percent}
	\caption{Bug Percentage in Maven Repository}
	\label{fig:bug-per} 
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.47]{corrplot.pdf}
  \caption{Correlation matrix plot for bug categories}
  \label{fig:corrplot}
\end{figure}

>>>>

\author{
{\rm Dimitris Mitropoulos,Vassilios Karakoidas,Panos Louridas}\\
{\it Department of Management Science and Technology,
Athens University of Economics and Business}\\
{\tt dimitro@aueb.gr, bkarak@aueb.gr, louridas@aueb.gr}
%\and
%{\rm Vassilios Karakoidas}\\
%Department of Management Science and Technology,
%Athens University of Economics and Business
%\and
%{\rm Panos Louridas}\\
%Department of Management Science and Technology,
%Athens University of Economics and Business
\and
{\rm Georgios Gousios}\\
{\it Software Engineering Research Group,
Delft University of Technology}\\
{\tt G.Gousios@tudelft.nl}
\and
{\rm Diomidis Spinellis}\\
{\it Department of Management Science and Technology,
Athens University of Economics and Business}\\
{\tt dds@aueb.gr}
}

@@

\begin{figure}[t]
  \begin{center}
    \includegraphics[scale=0.73]{figures/arch.pdf}
  \end{center}
  \caption{The Data Processing Architecture}
  \label{fig:arch}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[scale=0.37]{version_count.pdf}
	\caption{Distribution of Version Count Among Project Population}
	\label{fig:version-count}
\end{figure}

@@

\begin{table*}[t]
\centering
\caption{Bug Categorisation According to FindBugs}
\label{tbl:bug-cat}
\begin{tabular}{l p{29em}}
\hline
Category & Description\\
\hline
Bad Practice & Violations of recommended and essential
coding practice. \\
Correctness & Involves coding misting a way that is particularly different from the other bug sakes resulting in code
that was probably not what the developer intended. \\
Experimental & Includes unsatisfied obligations. For instance,
forgetting to close a file. \\
Internationalization (i18n) & Indicates the use of non-localized methods. \\
Multi-Threaded ({\sc mt}) Correctness & Thread synchronization issues. \\
Performance & Involves inefficient memory usage allocation, usage 
of non-static classes. \\
Style & Code that is confusing, or
written in a way that leads to errors.\\
Malicious Code & Involves variables or fields exposed to classes that should
not be using them. \\
Security & Involves input validation issues, unauthorized database connections
and others. \\
\hline
\end{tabular}
\end{table*}

@@

\begin{figure}[t]
	\centering
	\includegraphics[scale=0.35]{bug_percent}
	\caption{Bug Percentage in Maven Repository}
	\label{fig:bug-per} 
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.43]{corrplot.pdf}
  \caption{Correlation matrix plot for bug categories}
  \label{fig:corrplot}
\end{figure}
